---
title: "R_P10_2048046"
author: "R Akhilandeshwari"
date: "4/12/2021"
output:
  pdf_document: default
  html_document: default
---

```{r}
#Installing the packages
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
#install.packages('factoextra')
library(factoextra) # clustering visualization
library(dendextend) # for comparing two dendrograms
```

```{r}
#Loading the Dataset
df <- USArrests
```

```{r}
#Omitting the null values
df <- na.omit(df)
```

```{r}
#Scaling the values
scale(df)
head(df)
```

```{r}
# Dissimilarity matrix
d <- dist(df, method = "euclidean")

# Hierarchical clustering using Complete Linkage
hc1 <- hclust(d, method = "complete" )

# Plot the obtained dendrogram
plot(hc1, cex = 0.6, hang = -1)
```

```{r}
#With the agnes function you can also get the agglomerative coefficient, which measures the amount of clustering structure found 
# Compute with agnes
hc2 <- agnes(df, method = "complete")

# Agglomerative coefficient
hc2$ac
```

```{r}
# methods to assess
m <- c( "average", "single", "complete", "ward")
names(m) <- c( "average", "single", "complete", "ward")

# function to compute coefficient
ac <- function(x) {
  agnes(df, method = x)$ac
}

map_dbl(m, ac)
```
**We can see that, the ward type of linkage is giving good coeffficient value**

```{r}
#We can visualize the dendrogram
hc3 <- agnes(df, method = "ward")
pltree(hc3, cex = 0.6, hang = -1, main = "Dendrogram of agnes") 
```

```{r}
# compute divisive hierarchical clustering
hc4 <- diana(df)

# Divise coefficient; amount of clustering structure found
hc4$dc
```


```{r}
# plot dendrogram
pltree(hc4, cex = 0.6, hang = -1, main = "Dendrogram of diana")
```

```{r}
# Ward's method
hc5 <- hclust(d, method = "ward.D2" )

# Cut tree into 4 groups
sub_grp <- cutree(hc5, k = 4)

# Number of members in each cluster
table(sub_grp)
```

```{r}
USArrests %>%mutate(cluster = sub_grp) %>%head
```

```{r}
plot(hc5, cex = 0.6)
rect.hclust(hc5, k = 4, border = 2:5)
```

```{r}
#The fviz_cluster function from the factoextra package to visualize the result in a scatter plot
fviz_cluster(list(data = df, cluster = sub_grp))
```

```{r}
# Cut agnes() tree into 4 groups
hc_a <- agnes(df, method = "ward")
cutree(as.hclust(hc_a), k = 4)
```

```{r}
# Cut diana() tree into 4 groups
hc_d <- diana(df)
cutree(as.hclust(hc_d), k = 4)
```

```{r}
#The function tanglegram plots two dendrograms, side by side, with their labels connected by lines.

# Compute distance matrix
res.dist <- dist(df, method = "euclidean")

# Compute 2 hierarchical clusterings
hc1 <- hclust(res.dist, method = "complete")
hc2 <- hclust(res.dist, method = "ward.D2")

# Create two dendrograms
dend1 <- as.dendrogram (hc1)
dend2 <- as.dendrogram (hc2)

tanglegram(dend1, dend2)
```

```{r}
dend_list <- dendlist(dend1, dend2)

tanglegram(dend1, dend2,
  highlight_distinct_edges = FALSE, # Turn-off dashed lines
  common_subtrees_color_lines = FALSE, # Turn-off line colors
  common_subtrees_color_branches = TRUE, # Color common branches 
  main = paste("entanglement =", round(entanglement(dend_list), 2))
  )
```
**The entaglement is 0.07 which is approximately equal to 0. So, the aligmnet between the complete and the ward measures is good**

```{r}
#Elbow method to know the optimal clusters
fviz_nbclust(df, FUN = hcut, method = "wss")
```
**The optimal clusters starts from 3 decreasing as we increase the cluster numbers**

```{r}
fviz_nbclust(df, FUN = hcut, method = "silhouette")
```
**When the number of clusters are 2, the silhouse width is more. Implies that, for the cluster size 2,we have good and optimised clustering effect.**

```{r}
gap_stat <- clusGap(df, FUN = hcut, nstart = 25, K.max = 10, B = 50)
fviz_gap_stat(gap_stat)
```
**As observed from the graph, we have optimal gap statistic when cluster size is 2.**

