---
title: "FACTOR ANALYSIS"
author: "R Akhilandeshwari"
date: "5/10/2021"
output: html_document
---

```{R}
setwd('C:/Desktop/MVA/FACTOR ANALYSIS/')
getwd()
```
# Problem statement:

<br>

##   Suppose a researcher wants to determine the underlying benefits consumers seek from the purchase of a shampoo. A sample of 30 respondents was interviewed. The respondents were asked to indicate their degree of agreement with the following statements using a 7 point scale (1: strongly disagree, 7: strongly agree)

<br>

## x1:It is important to buy a shampoo that prevents hair fall

<br>

## X2:I like a shampoo that gives shiny hair

<br>

## X3:A shampoo should strengthen the roots of your hair

<br>

## X4:I prefer shampoo that decelerates the greying of hair

<br>

## X5:Prevention of hair splitting is not an important as far as shampoo is considered

<br>

# X6:A shampoo should make hair attractive

<br>

```{r}
data<- read.csv('Shampoo.csv')
head(data)
```

<br>

```{r}
# Removing the respondent column
shampoo1 <-data[-1]
head(shampoo1)
```

<br>

## find eigen value based on this decide Number of PC's 
## No. PC = eigen values > 1 for our example PC's = 2

<br>

```{r}
print(cor(shampoo1))
eg <- eigen(cor(shampoo1))
print(eg$values)
print(eg$vectors)
```
<br>

## PCA

<br>

```{r}
fit <- factanal(shampoo1, 2, rotation="varimax", scores = "regression")
fit
```

<br>

```{r}
fit$scores[,1:2]
```
<br>

```{R}
#p-value is 0.266 > 0.05 so 2 factors are not sufficient
fit2 <- factanal(shampoo1, 3, rotation="varimax", scores = "regression")
fit2
```

<br>

## 42% variance explained by factor1 only\
## 74% variance was explained by PC1 and PC2 only\
## 80% variance was explained by 3 pc's

<br>

## to know contribution variables in each factors

<br>
```{r}
load2 <- fit2$loadings[,1:3]
load2
```

<br>

## In factor1 X1, X3 and X5 variables were contribytes more\
## In factor2 X2, X4 and X6 variables were contributes more\

<br>

```{r}
fit2$scores[,1:3]
fit2
```

# These score use for as a independent variables\









