---
title: "R_P6_2048046"
author: "R Akhilandeshwari"
date: "2/26/2021"
output:
  word_document: default
  html_document: default
---

1.Load mtcars dataset
```{r}
data(mtcars)
head(mtcars)
```

2.install ridge and glmnet packages
```{r}
#install.packages("ridge")
library(ridge)
#install.packages("glmnet")
library(glmnet)
```

3.Perform the exploratory data analysis
```{r}
?mtcars
```
**The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).**

**This data frame has 32 observations on 11 (numeric) variables.**

**[, 1]	mpg	Miles/(US) gallon**
**[, 2]	cyl	Number of cylinders**
**[, 3]	disp	Displacement (cu.in.) **
**[, 4]	hp	Gross horsepower**
**[, 5]	drat	Rear axle ratio**
**[, 6]	wt	Weight (1000 lbs)**
**[, 7]	qsec	1/4 mile time**
**[, 8]	vs	Engine (0 = V-shaped, 1 = straight)**
**[, 9]	am	Transmission (0 = automatic, 1 = manual)**
**[,10]	gear	Number of forward gears **
**[,11]	carb	Number of carburetors **

```{r}
str(mtcars)
```
**The mtcars dataset contains, 32 records with 11 attributes. All attributes are of numeric form **

```{r}
colSums(is.na(mtcars))
```
**There are no missing values in the mtcars dataset**

```{r}
colSums(mtcars==" ")
```
**None of the columns contain the empty values**



```{r}
boxplot(mtcars)
boxplot(mtcars$hp)
boxplot(mtcars$wt)
boxplot(mtcars$qsec)
```

```{r}
#install.packages("funModeling")
library("funModeling")
plot_num(mtcars)
#hist(mtcars$hp)
```

```{r}
#install.packages("GGally")
library(GGally)
ggcorr(mtcars, label = T)
```
**The mpg is negatively correlated to cyl,disp,hp,wt and carb. And its not highly  correlated to qsec. So, while predicting the mpg of the vechicle, I am excluding the qsec attribute**


4. 

```{r}
#define response variable
y <- mtcars$mpg

#define matrix of predictor variables
x <- data.matrix(mtcars[, c('cyl','disp','hp','drat','wt','vs','gear','carb')])
```


```{r}
#fit ridge regression model
model <- glmnet(x, y, alpha = 0)

#view summary of model
summary(model)
```

4.Choose optimum lambda value

```{r}
#perform k-fold cross-validation to find optimal lambda value
cv_model <- cv.glmnet(x, y, alpha = 0)

#find optimal lambda value that minimizes test MSE
best_lambda <- cv_model$lambda.min
best_lambda
```
**The lambda value that minimizes the test MSE turns out to be 1.893**

```{r}
#produce plot of test MSE by lambda value
plot(cv_model) 
```

```{r}
#find coefficients of best model
best_model <- glmnet(x, y, alpha = 0, lambda = best_lambda)
coef(best_model)
```
```{r}
#produce Ridge trace plot
plot(model, xvar = "lambda")
```
```{r}
#use fitted best model to make predictions
y_predicted <- predict(model, s = best_lambda, newx = x)

#find SST and SSE
sst <- sum((y - mean(y))^2)
sse <- sum((y_predicted - y)^2)

#find R-Squared
rsq <- 1 - sse/sst
rsq
```
**The R-squared turns out to be 0.8408. That is, the best model was able to explain 84.08% of the variation in the response values of the training data.**


