---
title: "TWO_WAY_MANOVA"
author: "R Akhilandeshwari"
date: "3/17/2021"
output: html_document
---

```{r}
library(car)
data("Soils")
attach(Soils)
View(Soils)
```
```{r}
#install.packages("MASS")
library(MASS)
```

```{r}
?Soils
```


```{r}
summary(Soils)
```
```{r}
str(Soils)
```
*All the given attributes are in numeric type except group.contour,depth,gp, block which are in Factor type*

```{r}
levels(Soils$Group)
```

```{r}
levels(Soils$Contour)
```
```{r}
levels(Soils$Depth)
```
```{r}
levels(Soils$Gp)
```
```{r}
levels(Soils$Block)
```
*There are 12 groups of soil varities at 3 Contour with 4 different depth bins. The soil type is classified to 4 blocks and there are 12 different Gp*


```{r}
Soil.model <- lm(cbind(pH,N,P,Ca)~Contour *Depth *1,data=Soils)
summary(Soil.model)
```
*The depth 30-90 have significant impact on the Ph value of the soil whereas the depth 10-30 have least significant impact.*

*The depth 10-90 have significant on the Nitrogen value of the soil whereas the Contour Slope has least significant impact.*

*The depth 10-90 and the contour slope, top have the significant impact on the Phosphorous value of the soil.*

*The depth 10-90 have significant on the Calcium value of the soil whereas the Contour Top has least significant impact.*

```{r}
Manova(Soil.model, multivariate=TRUE, type= c("III"), test=("Wilks"))
```
*For the type III  Wilks MANOVA test the p-value less than 0.05. Therefore, there is significant impact of the contour and the depth of the soils in its PH,N,P,Ca values*


```{r}
Manova(Soil.model, multivariate=TRUE, type = c("II"), test=("Wilks"))
```
*For the type II  Wilks MANOVA test the p-value less than 0.05. Therefore, there is significant impact of the contour and the depth of the soils in its pH,N,P,Ca values*



*Inference: The Contour and the depth of the soil have the impact on the differences in the pH,N,p,Ca levels of soil.*