---
title: "R_P2_2048046"
author: "R Akhilandeshwari"
date: "1/25/2021"
output: word_document
---

1. Create a vector different data types(Logical, Numeric, Integer, Complex,Character) and display their class and typeof  each datatype.
```{r}
V_LOG <- c(TRUE, TRUE, FALSE, FALSE)
class(V_LOG)
V_NUM<-c(23.4, 8, 5.6, 3)
class(V_NUM)
V_INT<-c(8L,24L,33L,367)
typeof(V_INT)
V_COM<-c(1+3i, 2+4i)
typeof(V_COM)
V_CHAR<-c("SAILAJA","RAMU","KALPANA")
typeof(V_CHAR)
```

2. Get and print the current working directory

```{r}
getwd()
```
```{r}
setwd("C:/Users/akhil/OneDrive/Desktop/R/P2")
```

```{r}
getwd()
```
3. Create this file using windows notepad by copying and pasting this data. Save the file as student.csv

S.No ,Sname, Degree, Total.marks, Grade
1,Andrew,UG,435,B
2,Babita,UG,210,D
3,Cathy,UG,459,A
4,Dominic,UG,542,A
5,Elsa,PG,520,B
6,Franko,PG,320,C
7,Gorang,UG,205,D 
8,Harsha,PG,325,C

4.Save this file in the  current working directory

5.Read the csv file in your current working directory
```{r}
data<-read.csv("student.csv")
data
```
6.Check whether your  CSV file is a dataframe and also check the number of rows and columns
```{r}
print(is.data.frame(data))
print(ncol(data))
print(nrow(data))
```
7. Apply all the functions sum(),mean(),sqrt()  related to dataframe
```{r}
sum(data$Total.marks)
mean(data$Total.marks)
sqrt(data$Total.marks)
cor(data$S.No,data$Total.marks)
var(data$Total.marks)
sd(data$Total.marks)
range(data$Total.marks)
min(data$Total.marks)
max(data$Total.marks)
prod(data$Total.marks)
```
8.Get the highest marks from the data frame
```{r}
max(data$Total.marks)
```
9. Get the details of the person with highest marks
```{r}
subset(data, Degree == 'PG')
```
10. Get all the students in UG degree whose marks is greater than 300
```{r}
subset(data, Total.marks > 300)
```
11. Add one more vector  Date_ of_ Joining(DOJ)  to the already existing dataframe 
```{r}
data$DOJ<-c('2012-01-01','2017-01-01','2020-01-03','2018-01-15',
            '2015-08-06','2017-01-01','2019-03-24','2017-05-17')
data
```
12. Get the details of the students who have joined after 2017
```{r}
filt_data<-subset(data, as.Date(DOJ) > as.Date("2017-01-01"))
filt_data
```
13. Write the filtered data into a new file
```{r}
write.csv(filt_data,"student_dupl.csv")
```

```{r}
read.csv('student_dupl.csv')
```