---
title: "R_P3_2048046"
author: "R Akhilandeshwari"
date: "1/29/2021"
output: word_document
---

```{r}
setwd("C:/Desktop/R/P3")
getwd()
```
1.Import the LungCapData into R and attach it
```{r}
library("readxl")
data<-read_excel("Lungcap.xlsx")
data
```
2. Find the class and typeof Age and Height 
```{r}
typeof(data$Age)
class(data$Height)
```
3. Find the summary of the dataset
```{r}
summary(data)
```
4.Find the strength of the relationship between Age and Height (Hint:Using  Correlation)
```{r}
cor(data$Age,data$Height)
```
5.Perform a scatterplot for the above (Qn.4)
```{r}
plot(data$Age,data$Height)
```
6. Add a title to the plot and Label  x-axis and y-axis
```{r}
plot(data$Age,data$Height,xlab="AGE OF PATIENT",ylab="HEIGHT OF PATIENT",main="AGE Vs HEIGHT")
```
7.Rotate the values on the y-axis and also change the limits of x-axis and y-axis
```{r}
library(ggplot2)
pl<-ggplot(data,aes(Age, y=Height)) + geom_point()
pl+theme(axis.text.y = element_text(angle=60))+scale_x_continuous(limits = c(2, 20))+scale_y_continuous(limits = c(20, 100))
```
8.  Remove the axes of the plot and relabel these axes
```{r}
pl+theme(axis.text.x = element_blank(),
         axis.ticks.x = element_blank(),
         axis.text.y = element_blank(),
         axis.ticks.y = element_blank())+labs(x="AGE OF PATIENT",y="HEIGHT OF PATIENT")
```
9.Change the size of the plotting characters
```{r}
pl+geom_point(size=8)
```

10.Change the color of the characters to red
```{r}
pl+theme(axis.title.x = element_text(colour = "red"),
          axis.title.y = element_text(colour = "green"))
```
11.Draw the regression line to the plot predicting height using age
```{r}
pl+geom_smooth(method=lm)
```
12.Change the color of the line to blue and the width of the line
```{r}
pl+geom_smooth(method=lm,size=2.3,color="blue") 
```
13.Change the font of the plotting characters
```{r}
windowsFonts(A = windowsFont("Times New Roman")) 
pl+theme(text=element_text(family="A", face="bold", size=12))
```

14.Change  the color of the plotting characters
```{r}
pl+geom_point(color="red")
```
15.Identify gender on the plot for the age male and female 
```{r}
pl + geom_point(aes(shape=factor(Gender),colour=factor(Gender)))
```