---
title: "R_P7_2048046"
author: "R Akhilandeshwari"
date: "3/15/2021"
output: html_document
---

*1.Download the dataset BOSTON.csv*
```{r}
setwd('C:/Desktop/R/P7')
#library(MASS)
boston=read.csv("boston.csv")
head(boston)
```
```{r}
str(boston)
```
```{r}
colSums(is.na(boston))
```
**There are no mssing values in the data**
```{r}
colSums(boston=='')
```
**The data doesn't contains NA values**

*2.MEDV is the output /target variable i.e price of the house to be predicted*
```{r}
pred = boston["MEDV"]
head(pred)
```

*3. Using the plot commands, plot the latitude and longitude of each of our census tracts*
```{r}
library("ggplot2")
boston$CHAS<-as.factor(boston$CHAS)
ggplot(boston,aes(x=LON,y=LAT,color=CHAS))+geom_point()+labs(title="Latitude & Longitude of Census Tracts")
```
4. Show all the points that lie along the Charles River in a blue colour.
```{r}
library("dplyr")
ch_1<-boston%>%
filter(CHAS==1)
ggplot(ch_1,aes(x=LON,y=LAT))+geom_point(color="blue")+labs(title="Charles River",x="Longitude",y="Latitude")
```
```{r}
plot(boston$LON, boston$LAT, main = "Charles River in a blue colour",  xlab="Longitude", ylab="Latitude", col="#bbbbbb", pch=20, cex= 0.7)
points(boston$LON[boston$CHAS==1], boston$LAT[boston$CHAS==1], col="#005fba", pch=16)
```
5.Apply Linear Regression by plotting the relationship between latitude and house prices and the longitude and the house prices.
```{r}
ggplot(data=boston,aes(x=LON,y=MEDV))+geom_smooth(method="lm")+labs(title="Longitude & House Prices")
```
```{r}
ggplot(data=boston,aes(x=LAT,y=MEDV))+geom_smooth(method="lm")+labs(title="Latitude & House Prices")
```
```{r}
latlonlm = lm(MEDV ~ LAT + LON, data=boston)
summary(latlonlm)
```
**The regression equation is MEDV=-40.268LON+8.046LAT-3178.472 The value of adjusted Rˆ2 is 0.1072 which means the model can explani 10.72% variability in MEDV.**

6.Apply Regression Tree to the problem and draw conclusions from it.
```{r}
ggplot(data=boston)+geom_density(aes(x=MEDV))+labs(title="Distribution Plot of MEDV")
```
**The pllot iss normally distributed, which is slightly left skewed**

```{r}
set.seed(155)
spts=sample(1:nrow(boston),0.7*nrow(boston))#70% Training Data
train<-boston[spts,]
test<-boston[-spts,]
```

```{r}
linreg = lm(MEDV ~ LAT + LON + CRIM + ZN + INDUS + CHAS + NOX + RM + AGE + DIS + RAD + TAX + PTRATIO, data=train)
summary(linreg)
```
```{r}
linreg.pred = predict(linreg, newdata=test)
linreg.sse = sum((linreg.pred - test$MEDV)^2)
linreg.sse
```
```{r}
library(rpart)
library(rpart.plot)
library(caTools)
```

```{r}
tree = rpart(MEDV ~ LAT + LON + CRIM + ZN + INDUS + CHAS + NOX + RM + AGE + DIS + RAD + TAX + PTRATIO, data=train)
prp(tree)
```
```{r}
summary(tree)
```
```{r}
predicted<-predict(tree,test)
#install.packages("Metrics")
library(Metrics)
actual<-test$MEDV
rmse(actual,predicted)
```
```{r}
predict1<-predict(tree)
actual1<-train$MEDV
rmse(actual1,predict1)
```

