---
title: "R_P8_2048046"
author: "R Akhilandeshwari"
date: "3/19/2021"
output: html_document
---

#Demonstrate step by step procedure of  Random Forest using R choosing any Data Set of your choice

**Setting the Directory**
```{r}
setwd('C:/Desktop/R/P8')
getwd()
```
**Loading the data**
```{r}
d<-read.csv('BankChurners.csv')
#fb<-read.csv('pseudo_facebook.csv')
tail(d) 
```

**Understanding the data**
```{r}
str(d)
```
**There are 23 attributes in the data with 10127 observations in our data.**


**Checking the Null values in the data**
```{r}
colSums(is.na(d))
```
**There are no null values data **

```{r}
library(dplyr)
d<-select(d, -c(CLIENTNUM))
```

**Converting the factor to numeric format**
```{r}
d$Attrition_Flag<- as.character(d$Attrition_Flag )
d$Attrition_Flag[d$Attrition_Flag=="Existing Customer"]<-1
d$Attrition_Flag[d$Attrition_Flag=="Attrited Customer"]<-0
d$Attrition_Flag <- as.numeric(d$Attrition_Flag)
typeof(d$Attrition_Flag)
unique(d$Attrition_Flag)
```

```{r}
library("ggplot2")
d$Gender<-as.factor(d$Gender)
ggplot(d,aes(x=Credit_Limit ,y=Avg_Utilization_Ratio ,color=Gender))+geom_point()+labs(title="Credit Limit Vs AVG utilization Ratio ")
```


```{r}
#install.packages("randomForest")
library(randomForest)
```

```{r}
#make this example reproducible
set.seed(10000)
sd <-sample(2,nrow(d),replace = T,prob = c(0.6, 0.4))
sd.dev <- d[sd==1,]
sd.val <- d[sd==2,]

#fit the random forest model
model <- randomForest(formula = Attrition_Flag ~ .,data = sd.dev)

model
```

```{r}
#find number of trees that produce lowest test MSE
which.min(model$mse)
```
```{r}
#find RMSE of best model
sqrt(model$mse[which.min(model$mse)]) 
```
**The average difference between the actual and predicted might be 2.600447e-15**

```{r}
#plot the test MSE by number of trees
plot(model)
```

```{r}
#Predicting
pred=round(predict(model,sd.val))
tail(pred)
```

```{r}
library(caret)
actual<-sd.val$Attrition_Flag
cat("MAE",MAE(pred, actual),"\n")
cat("RMSE",RMSE(pred, actual),"\n")
```
```{r}
library(ROCR)
ROCRpred <- prediction(pred,actual)
ROCRperf <- performance(ROCRpred, measure = "tpr", x.measure = "fpr")

plot(ROCRperf, colorize = TRUE, text.adj = c(-0.2,1.7), print.cutoffs.at = seq(0,1,0.1))
```
```{r}
auc<-performance(ROCRpred,measure="auc")
auc<-auc@y.values[[1]]
auc
```
**The model is 100% Accurate for predicting whether the customer is existing or churned customer**


**Source: **
*https://www.guru99.com/r-random-forest-tutorial.html#1*
*https://www.statology.org/random-forest-in-r/*







